---
title: "Feasability trait sampling in LiMMBo"
author: "Hannah Meyer"
date: "18/07/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Set-up
```{r libraries}
#### libraries ##
library(ggplot2)
```

```{r functions}
#### functions ##
subsetSampling <- function(P, s, minCooccurrence, verbose=FALSE) {
    if (verbose) cat("Sampling for", P, "traits\n")
    counter <- 1
    counts <- matrix(0, nrow=P, ncol=P)
    
    while (min(counts) < minCooccurrence) {
        newindex <- sample(P, s, replace=FALSE)
        counts[newindex, newindex] <-  counts[newindex, newindex] + 1
        counter <- counter + 1
    } 
    return(list(counter=counter, counts=counts))
}

ttcooccurence <- function(nrtraits, nrtraitssampled) {
    1/nrtraits * 1/(nrtraits-1) * nrtraitssampled * (nrtraitssampled-1)
}
```


# 2. Simulate sampling as implemented in LiMMBo 0.1.4
```{r set parameters}
## parameters
set.seed(10)

# minimum number of co-occurence of trait pair
minCooccurrence <- 3
# number of traits
P <- seq(50,500,50)
# sub-sampling size
s <- c(10, 15)
```

```{r simulation, cache=TRUE}
simulatedSampling <- lapply(1:10, function(dummy) {
    tmp_P <- lapply(P, function(traits) {
        tmp_s <- lapply(s, function(subsample, traits) {
            subsetSampling(P=traits, s=subsample, 
                           minCooccurrence=minCooccurrence,
                           verbose=FALSE)
        }, traits=traits)
        counter <- sapply(tmp_s, function(x) x$counter)
        names(counter) <- paste("Subsample", s, sep="")
        counts <- lapply(tmp_s, function(x) x$counts)
        names(counts) <- paste("Subsample", s, sep="")
        return(list(counter=counter, counts=counts))
    })
    
    counter <- sapply(tmp_P, function(x) x$counter)
    colnames(counter) <- paste("Traits", P, sep="")
    counter <- reshape2::melt(counter)
    counts <- lapply(tmp_P, function(x) x$counts)
    names(counts) <- paste("Traits", P, sep="")
    return(list(counter=counter, counts=counts))
})
names(simulatedSampling) <- paste("rep", 1:10, sep="")
```

# 3. Reformat simulation results and plot 
```{r reformat and plot, cache=TRUE}
counter <- do.call(rbind, lapply(simulatedSampling, function(x) x$counter))
colnames(counter) <- c("Subsample", "Traits", "Bootstraps")
traitCosampling_empirical <- reshape2::acast(counter, Subsample ~ Traits, mean)
traitCosampling_empirical_sd <- reshape2::acast(counter, Subsample ~ Traits, sd)
counter$Traits <- as.factor(as.numeric(gsub("Traits", "", counter$Traits)))


p_counter <- ggplot()
p_counter + geom_boxplot(data=counter, 
                                      aes(x=Traits, y=Bootstraps,
                                          color=as.factor(Subsample))) +
    scale_color_manual(values=c('#377eb8','#4daf4a'), name="Type") +
    theme_bw()
